Clustering and Parameter Estimation for the Popularity Adjusted Block Model

### 2020-07-22 summary.Rmd
still working on comparisons

results.df %>% 
  dplyr::group_by(n) %>% 
  dplyr::summarise(med.err = median(error),
                   first.q = quantile(error, .25),
                   third.q = quantile(error, .75)) %>% 
  ggplot() + 
  labs(y = 'error') + 
  geom_line(aes(x = n, y = med.err)) + 
  geom_errorbar(aes(x = n, ymin = first.q, ymax = third.q))
```

@@

rmse.df %>% 
  dplyr::group_by(n) %>% 
  dplyr::summarise(median.rmse = median(rmse),
                   q1.rmse = quantile(rmse, .25),
                   q3.rmse = quantile(rmse, .75)) %>% 
  dplyr::ungroup() %>% 
  ggplot() + 
  geom_line(aes(x = n, y = median.rmse)) + 
  geom_errorbar(aes(x = n, ymin = q1.rmse, ymax = q3.rmse)) + 
  labs(y = 'RMSE')
```

>>>>

results.df %>% 
  dplyr::group_by(n) %>% 
  dplyr::summarise(med.err = median(error),
                   first.q = quantile(error, .25),
                   third.q = quantile(error, .75)) %>% 
  ggplot() + 
  # scale_y_log10() + 
  labs(y = 'error') + 
  geom_line(aes(x = n, y = med.err)) + 
  geom_errorbar(aes(x = n, ymin = first.q, ymax = third.q))
```

@@

rmse.df %>% 
  dplyr::group_by(n) %>% 
  dplyr::summarise(median.rmse = median(rmse),
                   q1.rmse = quantile(rmse, .25),
                   q3.rmse = quantile(rmse, .75)) %>% 
  dplyr::ungroup() %>% 
  ggplot() + 
  scale_y_log10() + 
  scale_x_log10() + 
  geom_line(aes(x = n, y = median.rmse)) + 
  geom_errorbar(aes(x = n, ymin = q1.rmse, ymax = q3.rmse)) + 
  labs(y = 'RMSE')
```
